---
output: html_document
params:
  input_pub_name: NA
  input_pub_date: NA
---
<style type="text/css">

div.statgov { 
color: rgb(0,71,133) !important;
}

div.statgov2 { 
color: rgb(0,71,133) !important;
font-weight: bold

}

div.pubs { 
color: orange !important;
}

div.pubs2 { 
color: orange !important;
font-weight: bold
}

div.open_data { 
color: green !important;
}

div.open_data2 { 
color: green !important;
font-weight: bold
}

div.key_date { 
color: red !important;
font-size: 20px;
font-weight: bold
}

div.key_date2 { 
color: red !important;
font-weight: bold
}

div.error { 
color: red !important;
font-size: 22px
}

body {
  font-family: Arial;
  font-size: 10pt;
}

h3 {
  font-family: Arial;
  font-size: 12pt;
}

h4 {
  font-family: Arial;
  font-size: 11pt;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lubridate)
library(tidyverse)

#date print function
dprint <- function(date_to_use, adjuster){
  new_date <- date_to_use - adjuster
  paste0(wday(new_date, label = TRUE, abbr = FALSE)," ", format(new_date, "%d %B %Y"))
}

#extract parameters to new objects
pub_name <- params$input_pub_name
pub_date <- ymd(params$input_pub_date)

#output: html_document
#params:
#  input_pub_name: NA
#  input_pub_date: NA

```

## **timetable for publication**
### **Publication: `r pub_name`**  
### **Date selected: `r dprint(pub_date,0)`**

```{r echo = FALSE}
pub_day <- wday(pub_date, label = TRUE, abbr = FALSE)
```

***
<div class = "key_date2">Key dates</div>
<div class = "statgov2">Statistical Governance</div>
<div class = "pubs2">Publications team</div>
<div class = "open_data2">Open data</div>
***

### **`r dprint(pub_date, 13)`**

#### *Analyst actions:*

* **Prior to today:**
If possible, review content of publication with the Communications Manager:<br>NSS.PHI-Communications@nhs.net
* Ensure the publication summary is in the relevant Health Topic folder for review 
at Key Messages Handling meeting by 3pm:<br>`Publications/HealthTopic/YourHealthTopic/PublicationName/yyyy-mm-dd`

***
### **`r dprint(pub_date, 12)`**

#### *Analyst actions:*

* Attend Key messages handling meeting.
* Give an overview of the publication. A completed Twitter Content Submission form is also required.

#### *Publications & SG Team Actions:*

<div class = "statgov">
* Attend Key messages handling meeting.
</div>

***
### **`r dprint(pub_date, 8)` - prior to 8am**

#### *Analyst actions:*

* Analyst finalises Publication Summary, Publication Report, Statistical Release (if appropriate) 
and all downloadable tables/files <div class = "open_data">(Excel and csv/Open Data)</div>
* Analyst completes the Disclosure Form and retains in team
* Editor checks the publication for accuracy and presentation and completes checklist on the Publication Report. 
* Service Manager (or equivalent) then gives the Approval for Release by signing the Publication Report 
* Provide Publications Team with narrative for all web pages within the topic area that 
need updated when the publication goes live using NSS.PHIWebsites@nhs.net 

#### *Publications & SG Team Actions:*

<div class = "pubs">
* Populate Weblink document with URLs and secure login details.
</div>

***
### **`r dprint(pub_date, 8)` - 8am**

#### *Analyst actions:*

* Place all files in shared directory by 8am, including all Open Data Files:
<br> `Publications/HealthTopic/YourHealthTopic/PublicationName/yyyy-mm-dd`)
* Editor advises Publications Team by 8:00am of this transfer via email: NSS.PHIPublications@nhs.net

#### *Publications & SG Team Actions:*
<div class = "pubs">
* Load publication files for 5 day Pre-Release-Access to secure folders by midday.
* Send Weblink document to analysts and Statistical Governance Team by midday.
</div>

***
### **`r dprint(pub_date, 7)`**

<div class = "key_date">5 Day PRA</div>

#### *Analyst actions:*

* *Note:* 5 day Pre Release Access can only be provided by ISD Director and
ISD Statistical Governance; exceptions to this need Head of Service approval.
* Where 5 day PRA for other individuals has been agreed with Head of Service/Service Manager/Statistical Governance,
send out email around 11:30 am.

#### *Publications & SG Team Actions:*
<div class = "statgov">
* Executive Office sends email with links for PRA, to all NHS Board CEs, Communications Manager.
* Email site links to ASD (Head, Deputy & PA) for PRA by 11:30 (as soon as checks are complete) and notify analysts.
</div>
<div class = "pubs">
* Prepare site for 5 day Pre-Release Access by 11:30am.
</div>

***
### **`r dprint(pub_date, 6)`**

<div class = "key_date">Handling meeting</div>

#### *Analyst actions:*

* Editor (or equivalent) to attend Handling Meeting, if required.  
This meeting is usually held at Gyle Square (teleconference with SG)
* If changes are required, advise Publications Team and provide the changes as soon as possible:
<br>NSS.PHIPublications@nhs.net
* If changes are required to Open Data content, contact Open Data team as soon as possible:<br>NSS.PHI-OpenData@nhs.net
* If no further changes are required, also advise Publications Team 

#### *Publications & SG Team Actions:*
<div class = "statgov">
* Facilitate Handling Meeting at Gyle Square.
</div>

***
### **`r dprint(pub_date, 5)`**

#### *Analyst actions:*

* Final Publication Summary, Report, Statistical Release (if appropriate) and 
Twitter content form and tables are placed in shared directory as soon as possible and no later than 12 noon:<br>
(`Dept/PHI Publications/yyyy-mm-dd/YourPublication/`)
* Editor advises Publications Team of this transfer via email:<br>
NSS.PHIPublications@nhs.net<br>by 12 noon. Even if there's no change, please advise Publications Team.
* *Note:* Publications Team will create PDF versions of the Publication Summary, Publication Report and
Statistical Release (if appropriate) and make available for Analyst to check.

#### *Publications & SG Team Actions:*
<div class = "pubs">
* Create PDF versions of the Publication Summary, Publication Report and Statistical Release (if appropriate)
and send to Analyst for checking.
* Reload any updated Excel files.
</div>
<div class = "open_data">
* If appropriate, send Publications Team URL for Open Data on CKAN:<br>nss.isdspnmanager@nhs.net
</div>

***
### **`r dprint(pub_date, 4)`**

#### *Analyst actions:*

* Check PDF versions and data files are the latest versions
* Notify Publications Team of any issues with the PDF versions/links etc as soon as possible and by Monday 12 noon at the latest. 

#### *Publications & SG Team Actions:*
<div class = "pubs">
* Create PDF versions and send to Analyst for checking.</div>

***
### **`r dprint(pub_date, 1)`**

#### *Analyst actions:*

* Continue to check all links and the PDF versions of the Publication Summary and Report.
* Publications Team must be advised of any issues as soon as possible and by 12 noon at the latest.

#### *Publications & SG Team Actions:*
<div class = "pubs">
* Finalise PDF versions and send to Analyst for checking by 9:00am.
* Final preparing of site for going live the following day.</div>

***
### **`r dprint(pub_date, 0)`**

<div class = "key_date">Publication date</div>

#### *Analyst actions:*

* Check that the website is live and correct for your publication at 9.30am.
* Review the SG News Release section (http://www.scotland.gov.uk/News/News-Today).

#### *Publications & SG Team Actions:*
<div class = "pubs">* Publications release at 9:30am on ISD Website.</div>
<div class = "statgov">* Check that the ISD website is live and correct.</div>
